---
title: "Secondary Analysis Method"
author: "Brett Longworth"
date: "1/7/2016"
output: html_document
---

This document describes the method I use to extract secondary standards from the database, normalize the data, calculate sigma and other statisics and display. Please check out the full code for the project for more detail. The code is in R, but I've tried to add explanations and comment as much as possible. The everyday code is broken up into functions to make it more flexible.

  The full package I use for this is at https://github.com/blongworth/secondaries.git. Please download a copy and have a look. Everything is written in R, and I use Rstudio as a development environment. I use the RODBC package for database access, the dplyr package for sorting and filtering data, and ggplot2 for plotting. The web applications use the shiny package for all of the interactive web magic.
  
## Getting the data

The procedure below is a linearized and simplified version of the code to extract secondary data.  Here, we'll get data for IAEA C-2.

### Load libraries and open a database connection.

```{r warning=FALSE, message=FALSE}
#Load Libraries
library(RODBC) #database
library(dplyr) #data manipulation
library(ggplot2) #plotting

#Load files
source("~/R/dbconfig.R") #DB connection info

#Open DB connection
  db <- odbcConnect(database, uid = uid, pwd = pwd)
```

### Get the data for C-2 (rec 1082). 

  I'm pulling only a few months of data to keep the results simple.

#### First, get the summary data

This is mostly straight SQL.

```{r}
 f <- sqlQuery(db, paste("
        SELECT target.rec_num, target.tp_num, target.osg_num, target.target_name, 
          wheel_pos.wheel_id, target.tp_date_pressed, graphite_lab.lab_name, 
          no_os.f_modern, no_os.f_int_error, no_os.f_ext_error, no_os.dc13,
          graphite.gf_co2_qty, no_os.q_flag, snics_results.sample_type, snics_results.sample_type_1
        FROM no_os, target, wheel_pos, graphite, graphite_lab, snics_results
        WHERE target.tp_num = no_os.tp_num 
          AND target.tp_num = wheel_pos.tp_num 
          AND target.tp_num = snics_results.tp_num
          AND target.osg_num = graphite.osg_num 
          AND target.graphite_lab = graphite_lab.lab_id
          AND target.rec_num = 1082 
		      AND target.tp_date_pressed > '2015-01-01'
          AND target.tp_date_pressed < '2015-04-01'
        "))
```

#### Then pull current and count data

These have to be pulled from the snics_raw table and summarized. Probably a better way to do this all in one query, but SQL isn't my forte.

```{r}
cur <- sqlQuery(db, paste("
        SELECT snics_raw.tp_num, AVG(le12c) AS le12c
        FROM snics_raw, target
        WHERE target.tp_num = snics_raw.tp_num
          AND ok_calc = 1
          AND target.rec_num = 1082 
          AND target.tp_date_pressed > '2015-01-01'
          AND target.tp_date_pressed < '2015-04-01'
          GROUP BY snics_raw.tp_num
        "))
  
count <- sqlQuery(db, paste("
        SELECT snics_raw.tp_num, SUM(cnt_14c) AS counts
        FROM snics_raw, target
        WHERE target.tp_num = snics_raw.tp_num
          AND ok_calc = 1
          AND target.rec_num = 1082 
          AND target.tp_date_pressed > '2015-01-01'
          AND target.tp_date_pressed < '2015-04-01'
          GROUP BY snics_raw.tp_num
        "))
  
odbcClose(db)

# Bind the three data frames together
f <- left_join(f, cur, by = "tp_num")
m <- left_join(f, count, by = "tp_num")
```

Here's a few lines of the data table so far:

```{r}
head(m)
```

## Data munging and statistics

### Normalization

To allow comparison of secondaries of differing Fm, the data are normalized such that perfect agreement with consensus is Fm 0. 

Normalized fm difference is defined as:

$\frac{Fm_{m}-Fm_{c}}{Fm_{c}}$

where $Fm_{m}$ is measured Fm and $Fm_{c}$ is consensus Fm.

#### First, define functions for normalized fm and sigma.

```{r}
#Calculate Sigma
sigma <- function(fmm,fmc,em,ec) {
  (fmm - fmc) /sqrt(em^2 + ec^2)
}

#Calculate normalized fm
normFm <- function (fmm, fmc) {
  (fmm - fmc) / fmc
}
```

#### Calculations and table formatting

Add max error, calculate sigma and normalized Fm. Next calculate things like max error and relative (fractional) errors. Figure out what system the data are from (one would think there'd be a field for this!), flag primaries, fix currents, etc...

```{r}
#Get data for a secondary standard and calculate fmdiff and
#sigma  using intcal results
  
# consensus fm and error from intcal table
fmc <- 0.4114 
ec <- 0.0003 

# add calculated fields to data table
out <- m %>% 
  mutate(merr = pmax(f_int_error, f_ext_error),
         normFm = normFm(f_modern, fmc),
         sigma = sigma(f_modern, fmc, merr, ec),
         #add relative error
         finterr = f_int_error/f_modern,
         fexterr = f_ext_error/f_modern, 
         fmaxerr = merr/f_modern, 
         #system
         system = ifelse(grepl("CFAMS", wheel_id), "CFAMS", "USAMS"),
         #fix CFAMS 12C
         le12c = ifelse(system == "USAMS", le12c * -1, le12c),
         #is primary?
         primary = ifelse(!is.na(sample_type_1) & sample_type_1 == "S",
                          TRUE, 
                          ifelse(!is.na(sample_type) & sample_type == "S", 
                                 TRUE, FALSE)), 
         #add data from intcal table
         rec_num = 1082,
         name = "IAEA C-2",
         fm_consensus = fmc) %>%
  #number of splits?
  group_by(osg_num) %>% #For each osg_num
  mutate(splits = n()) #Count occurrences to get number of splits
```

### Filtering

Data are filtered to minimize influence of size and Fm on assessment of data quality. Here, we also select only samples from the SPL that are not primary standards.

Depending on the script, I filter out bad points by a combination of sigma, normalized Fm, and relative reported error. q_flag isn't commonly used, but I filter out points that are flagged. Typically, secondaries less than 10 sigma, 2 percent in Fm away from the correct value and less than 10 percent fractional reported error are used.

Really, I should be researching and properly flagging bad points. For instance, poor quality primary standards are demoted to secondaries, which adds a population of poor-quality gas OX-I's to the secondary pool. Similarly, test samples are often not flagged in a consistent way. To be fair, there's no way to know if most types of unknowns are flyers, so leaving some bad data in is probably a valid estimate of overall quality. 
```{r}

#Filter data
out <- out %>% filter(
                primary == FALSE, #don't use normalizing ox-I
                f_modern > .1, f_modern < 1.6, #Select fm range
                gf_co2_qty > 40, gf_co2_qty < 300, #Select size range
                lab_name == "OSG", #Use only samples from the SPL
                is.na(q_flag), #Check for q_flag
                sigma < 10, sigma > -10, #Select reasonable sigmas
                normFm < 0.02, normFm > -0.02, #Select reasonable Fm
                fmaxerr < 0.10
              )
```

Here's a few lines of the data table after munging and calculating:

```{r}
head(out)
```

## Summary statistics

The summary fields below are mean normalized Fm (nFm) and it's standard deviation (nFm.s), mean sigma (sig), mean relative reported error (ferr) and the number of samples (N). I typically view ferr as the reported precision and nFm as the population distribution for repeated measures. The core of our "facility error" question is which of these should be reported and how the client should use them to estimate the precision and accuracy of their analysis.

```{r}

#Make summary table
out %>%
  group_by(system) %>%
  summarize(
    nFm = mean(normFm),
    nFm.s = sd(normFm),
    sig = mean(sigma),
    ferr = mean(fmaxerr),
    N = n()
    )
```

## Plotting

Add a simple histogram, broken out by system.
```{r SigmaHistogram, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
ggplot(out, aes(sigma)) + geom_histogram() + 
  facet_grid(system ~ .) + 
  ggtitle("Sigma Histogram")
```

The same by normalized fraction modern.
```{r FmHistogram, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
ggplot(out, aes(normFm)) + geom_histogram() + 
  facet_grid(system ~ .) + 
  ggtitle("Fm Histogram")