Secondary standard analysis
========================================================

`r as.character(format(Sys.Date(), format="%B %d, %Y"))`





```{r Setup, echo=FALSE, warning=FALSE, message=FALSE}

#Load Libraries
library(dplyr)
library(ggplot2)
library(knitr)
library(RODBC)

#Load files
source("~/R/dbconfig.R") #DB connection info
source("CalculateSecondaries.R") #Functions

#set parameters
from <- '2015-09-01'
to <- 'present' #present or date
sys <- 'both' #cfams, usams, ams1 or both
size <- c(40,300)

#Set digits for output
options(digits=4)

# Get fresh secondary data
#out <- getQCData(from, to, sys)

#Load QC data from file
load("qcData.rda")

#Filter data
out.s <- filter(out, primary == FALSE, # rec_num != 113385, #don't use normalizing ox-I
                f_modern > .1, f_modern < 1.6,
                as.Date(tp_date_pressed) >= as.Date(from),
                as.Date(tp_date_pressed) <= ifelse(to != 'present', to, Sys.Date()),
                gf_co2_qty > size[1], gf_co2_qty < size[2], #Select size range
                sigma < 10, sigma > -10, 
                lab_name == "OSG") #Use only samples from the SPL```
```

Analysis of performance of all secondary standards for `r sys` from `r from` to `r to`. Sample size is from `r size[1]` to `r size[2]`umol, outliers have been removed by sigma (-10 to 10) and normalized Fm (-0.02 to 0.02), and only secondaries Fm > .1 used.

* Mean Sigma for USAMS is `r mean(out.s$sigma[out.s$system=="USAMS"])`.
* Mean Sigma for CFAMS is `r mean(out.s$sigma[out.s$system=="CFAMS"])`.

Normalized fm difference is defined as:

$\frac{Fm_{m}-Fm_{c}}{Fm_{c}}$

where $Fm_{m}$ is measured Fm and $Fm_{c}$ is consensus Fm.


# Summary table

## By System

```{r, echo=FALSE, message=FALSE,}

#Make summary table
syssum <- out.s %>%
  group_by(system) %>%
  summarize(
    nFm = mean(normFm),
    nFm.s = sd(normFm),
    sig = mean(sigma),
    ferr = mean(fmaxerr),
    N = n()
    )

knitr::kable(syssum, digits = 4, caption = "Summary data for secondaries")


#print(table, floating=TRUE, type="html")
```


## By Secondary and System
```{r, echo=FALSE, message=FALSE, results='asis'}

#Make summary table
secsum <- out.s %>% 
  group_by(name, system) %>%
  summarise(
    fm.e = mean(fm_consensus),
    fm = mean(f_modern),
    fm.s = sd(f_modern),
    err = mean(merr),
    intrerr = intrErr(sd(f_modern), mean(merr)),
    d13c = mean(dc13),
    nFm = mean(normFm),
    nFm.s = sd(normFm),
    ferr = mean(fmaxerr),
    fintrerr = intrErr(sd(normFm), mean(fmaxerr)),
    sig = mean(sigma),
    sig.s = sd(sigma),
    N = n()
    )

knitr::kable(secsum, digits = 4, caption = "Summary data for all secondaries")
```


# Histograms

```{r SigmaHistogram, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

#Sigma histogram
#p <- qplot(sigma, data=out.s, geom="histogram", xlim=c(-10,10))
#p + ggtitle(paste("Sigma Histogram, ", sys, ", ", from))
ggplot(out.s, aes(sigma)) + geom_histogram() + 
  facet_grid(system ~ .) + 
  ggtitle(paste("Sigma Histogram, ", sys, ", ", from))
```


# Boxplots

Boxplots of secondaries ordered by Fm and separated by instrument. Boxes are 1st-3rd quartile, line is median, and whiskers indicate 1.5*IQD. 

```{r, SigmaBoxplots, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

#sigma boxplots
p <- ggplot(out.s, aes(name, sigma)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + facet_grid(system ~ .) + 
  ggtitle(paste("Sigma Boxplots, ", sys, ", ", from)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

#normfm boxplots
p <- ggplot(out.s, aes(name, normFm)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + facet_grid(system ~ .) + 
  ggtitle(paste("Normalized Fm difference Boxplots, ", sys, ", ", from)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```


## All secondaries by system

```{r, SystemBoxplots, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

#sigma boxplots
p <- ggplot(out.s, aes(system, sigma)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + ggtitle(paste("Sigma Boxplots for all secondaries by system")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

#normfm boxplots
p <- ggplot(out.s, aes(system, normFm)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + ggtitle(paste("Normalized Fm difference Boxplots for all secondaries by system")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```


# Fm vs Sigma

Sigma varies by Fm. First plot shows a regression through all data, 
which weights by N of secondaries, and second plot regression is 
through means of secondaries (whiskers show SD of mean).

```{r SigmavsRatio, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

#ratio vs sigma
p <- qplot(f_modern, sigma, color=system, shape=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + stat_smooth(method="lm", se=FALSE) +
  ggtitle(paste("Sigma vs Fm, ", sys, ", ", from))
  #scale_colour_manual(values=cbPalette)

p <- qplot(fm, sig, color=system, data=secsum)
p + geom_hline(yintercept=0) + geom_point() +
  geom_errorbar(aes(ymin=sig-sig.s, ymax=sig+sig.s), width=.02) + 
  geom_smooth(method="lm") + 
  geom_point(size=3) + ggtitle(paste("Sigma vs Fm, ", sys, ", ", from)) 
  #scale_colour_manual(values=cbPalette)

```


# Fm vs Normalized Fm error

Another way of looking at the same. Y-axis is now normalized Fm error ( (Fm - consensus) / consensus ).

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
#norm ratio vs ratio
qplot(f_modern, normFm, color=system, data=out.s) +
  geom_hline(yintercept=0) + geom_point() + geom_smooth(method="lm") +
  ggtitle(paste("NormFm vs Fm, ", sys, ", ", from))

ggplot(secsum, aes(x = fm, y = nFm, color=system)) +
  geom_hline(yintercept=0) + geom_point() + geom_smooth(method="lm") + 
  geom_errorbar(aes(ymin=nFm-nFm.s, ymax=nFm+nFm.s), width=.02) + geom_jitter(size=3) +
  ggtitle(paste("NormFm vs Fm, ", sys, ", ", from))
```



#Sample size vs sigma

```{r SizeHistogram, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

ggplot(out.s, aes(gf_co2_qty)) + geom_histogram() + 
  facet_grid(system ~ .) + 
  ggtitle(paste("Size Histogram, ", sys, ", ", from))
```

```{r sigmavsco2, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
p <- qplot(gf_co2_qty, sigma, color=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + #geom_smooth(method="lm") + 
  ggtitle(paste("Sigma vs umol CO2, ", sys, ", ", from))

p <- qplot(gf_co2_qty, normFm, color=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + #geom_smooth(method="lm") + 
  ggtitle(paste("Normfm vs umol CO2, ", sys, ", ", from))
```


# Date vs Sigma

```{r DateHistogram, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

ggplot(out.s, aes(tp_date_pressed)) + geom_histogram() + 
  facet_grid(system ~ .) + 
  ggtitle(paste("Date Histogram, ", sys, ", ", from))
```

```{r sigmavsdate,  echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
p <- qplot(tp_date_pressed, sigma, color=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + geom_smooth() + 
  ggtitle(paste("Sigma vs date, ", sys, ", ", from))

p <- qplot(tp_date_pressed, normFm, color=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + geom_smooth() + 
  ggtitle(paste("Normfm vs date, ", sys, ", ", from))
```


# System Precision

Looking at fractional error within samples to get an idea of system precision. This is error / fm. Internal (counting) error and external error compared. Ext/Int Precision Ratio looks at whether error is dominated by repeatability or counting statistics. I am not sure that these errors are comparable between systems, so please take with a grain of salt.

```{r precision,  echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}

qplot(name,finterr, color=system, data=out.s, geom="boxplot", ylim=c(0,.02), main="Internal precision") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
qplot(name,fexterr, color=system, data=out.s, geom="boxplot", ylim=c(0,.02), main="External precision") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
qplot(name,fexterr/finterr, color=system, data=out.s, geom="boxplot", main="Ext/Int Precision Ratio") +
  geom_hline(yintercept=1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



