---
output: html_document
---
Primary standard analysis
========================================================

`r as.character(format(Sys.Date(), format="%B %d, %Y"))`





```{r Setup, echo=FALSE, warning=FALSE, message=FALSE}

#Load Libraries
library(dplyr)
library(knitr)
library(RODBC)
library(ggplot2)

#Load files
source("~/R/dbconfig.R") #DB connection info
source("CalculateSecondaries.R") #Functions

#set parameters- from, to, sys not used if loading from file
from <- '2014-09-01'
to <- 'present' #present or date
sys <- 'both' #cfams, usams, ams1 or both
size <- c(40,300)

#Set digits for output
options(digits=4)

# Get fresh secondary data
#out <- getQCData(from, to, sys)

#Load QC data from file
load("qcData.rda")

#Filter data
out.s <- out %>% 
  filter(primary == TRUE,
         rec_num == 113385, #look at normalizing ox-I
         f_modern > .1, f_modern < 1.6,
         gf_co2_qty > size[1], gf_co2_qty < size[2]) %>% #Select size range
  mutate(month = ordered(months(tp_date_pressed), 
    c("September","October","November","December","January", "February", "March", "April", "May")))
  
```

Analysis of performance of primary standards for `r sys` from `r from` to `r to`. Sample size is from `r size[1]` to `r size[2]`umol, outliers have been removed by sigma (-10 to 10) and normalized Fm (-0.02 to 0.02).

* Mean Sigma for USAMS is `r mean(out.s$sigma[out.s$system=="USAMS"])`.
* Mean Sigma for CFAMS is `r mean(out.s$sigma[out.s$system=="CFAMS"])`.

Normalized fm difference is defined as:

$\frac{Fm_{m}-Fm_{c}}{Fm_{c}}$

where $Fm_{m}$ is measured Fm and $Fm_{c}$ is consensus Fm.


# Summary table


```{r, echo=FALSE, message=FALSE, results='asis'}

#Make summary table
secsum <- out.s %>% 
  group_by(name, system) %>%
  summarise(
    fm.e = mean(fm_consensus),
    fm.m = mean(f_modern),
    fm.s = sd(f_modern),
    merr.m = mean(merr),
    d13c = mean(dc13, na.rm = TRUE),
    sig = mean(sigma),
    sig.s = sd(sigma),
    intrerr = intrErr(sd(f_modern), mean(merr)),
    N = n()
    )

knitr::kable(secsum, digits = 4, caption = "Summary data for all primaries")

#Make summary table
monthsum <- out.s %>%
  group_by(system, month) %>%
  summarize(
    fm.e = mean(fm_consensus),
    fm.m = mean(f_modern),
    fm.s = sd(f_modern),
    sig.m = mean(sigma),
    sig.s = sd(sigma),
    merr.m = mean(merr),
    d13c = mean(dc13, na.rm = TRUE),
    intrerr = intrErr(sd(f_modern), mean(merr)),
    N = n()
  )

knitr::kable(monthsum, digits = 4, caption = "Summary data for all primaries by month")

#Make summary table
wheelsum <- out.s %>% 
  group_by(system, wheel_id) %>%
  summarize(
    date = mean(tp_date_pressed),
    fm.e = mean(fm_consensus),
    fm = mean(f_modern),
    fm.s = sd(f_modern),
    sig = mean(sigma),
    sig.s = sd(sigma),
    merr.m = mean(merr),
    intrerr = intrErr(sd(f_modern), mean(merr)),
    N = length(f_modern)) %>%
    arrange(system, as.Date(date))

knitr::kable(wheelsum, digits = 4, caption = "Summary data for all primaries by wheel")


```

# Plots of primary error by month

``` {r plots}
ggplot(data=wheelsum, aes(x=date, y=fm.s, color=system)) + 
  geom_point() + geom_smooth() +
  ggtitle("SD of OX-I by wheel")

ggplot(data=wheelsum, aes(x=date, y=merr.m, color=system)) + 
  geom_point() + geom_smooth() +
  ggtitle("reported error of OX-I by wheel")

ggplot(data=monthsum, aes(x=month, y=fm.s, fill=system)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  ggtitle("SD of OX-I by month")

ggplot(data=monthsum, aes(x=month, y=merr.m, fill=system)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  coord_cartesian(ylim = c(0.002, 0.004)) +
  ggtitle("reported error of OX-I by month")

ggplot(data=out.s, aes(x=month, y=f_ext_error/f_int_error, fill=system)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  coord_cartesian(ylim = c(1, 2)) +
  ggtitle("Error ratio by month")

ggplot(data=out.s, aes(x=month, y=f_ext_error, fill=system)) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
#  coord_cartesian(ylim = c(1, 2)) +
  ggtitle("Error ratio by month")

p <- qplot(tp_date_pressed, f_modern, color=system, data=out.s)
p + geom_hline(yintercept=1.0398) + geom_point() + geom_smooth(span=1) + 
  ggtitle(paste("Mean fm error vs date, ", sys, ", ", from))
```

# System Precision

Looking at fractional error within samples to get an idea of system precision. This is error / fm. Internal (counting) error and external error compared. Ext/Int Precision Ratio looks at whether error is dominated by repeatability or counting statistics. I am not sure that these errors are comparable between systems, so please take with a grain of salt.

```{r precision,  echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}

ggplot(out.s, aes(counts, finterr)) +
  geom_point(aes(shape = system, color = system)) + scale_shape(solid = FALSE) +
  #scale_y_continuous(limits = c(.0015, .0025)) + 
  ggtitle("Internal precision") 
ggplot(out.s, aes(le12c, finterr)) +
  geom_point(aes(shape = system, color = system)) + scale_shape(solid = FALSE) +
  #scale_y_continuous(limits = c(.0015, .0025)) + 
  ggtitle("Internal precision") 
ggplot(out.s, aes(counts, fexterr)) +
  geom_point(aes(shape = system, color = system)) + scale_shape(solid = FALSE) +
  #scale_y_continuous(limits = c(.0015, .0025)) + 
  ggtitle("External precision") 
ggplot(out.s, aes(le12c, fexterr)) +
  geom_point(aes(shape = system, color = system)) + scale_shape(solid = FALSE) +
  #scale_y_continuous(limits = c(.0015, .0025)) + 
  ggtitle("External precision") 
ggplot(out.s, aes(counts, fexterr/finterr)) +
  geom_point(aes(shape = system, color = system)) + scale_shape(solid = FALSE) +
  #scale_y_continuous(limits = c(.99, 1.01)) + 
  ggtitle("Ext/Int Precision Ratio") +
  geom_hline(yintercept=1) 
ggplot(out.s, aes(le12c, fexterr/finterr)) +
  geom_point(aes(shape = system, color = system)) + scale_shape(solid = FALSE) +
  #scale_y_continuous(limits = c(.99, 1.01)) + 
  ggtitle("Ext/Int Precision Ratio") +
  geom_hline(yintercept=1) 
```

