---
runtime: shiny
output: html_document
---


Secondary standard analysis
========================================================

`r as.character(format(Sys.Date(), format="%B %d, %Y"))`



```{r Setup, echo=FALSE, warning=FALSE, message=FALSE}

#Load Libraries
library(dplyr)
library(ggplot2)
library(knitr)
library(RODBC)

#Load files
#source("~/R/dbconfig.R") #DB connection info
#source("CalculateSecondaries.R") #Functions

#Functions
#calculate intrinsic error
intrErr <- function(totErr, targErr) {
  ifelse (totErr < targErr, NA, sqrt(totErr^2 - targErr^2))
}

#Set digits for output
options(digits=4)

# Get fresh secondary data
#out <- getQCData(from, to, sys)

#Load QC data from file
load("./qcData.rda")

out <- filter(out, primary == FALSE, #don't use normalizing ox-I
                lab_name == "OSG", #Use only samples from the SPL
                is.na(q_flag), #Check for q_flag
                sigma < 10, sigma > -10, #Select reasonable sigmas
                normFm < 0.02, normFm > -0.02, #Select reasonable Fm
                fmaxerr < 0.10
              )
```


## Filter data

Use these widgets to filter secondary data as desired

```{r echo = FALSE}
dateRangeInput('date',
               label = 'Date Range',
               start = Sys.Date() - 90, 
               end = Sys.Date(),
               max = Sys.Date())
sliderInput("size", "Graphite Size (umol)",
            1, 500, value = c(40,300))
sliderInput("fm", "Fm Range",
            0, 2, value = c(.1,1.6), step = 0.05)
 
out.s <- reactive({
    # Due to dplyr issue #318, we need temp variables for input values
    mindate <- input$date[1]
    maxdate <- input$date[2]
    minsize <- input$size[1]
    maxsize <- input$size[2]
    minfm <- input$fm[1]
    maxfm <- input$fm[2]
    
    # Apply filters
    out %>%
      filter(
        as.Date(tp_date_pressed) >= as.Date(mindate),
        as.Date(tp_date_pressed) <= as.Date(maxdate),
        gf_co2_qty >= minsize,
        gf_co2_qty <= maxsize,
        fm_consensus >= minfm,
        fm_consensus <= maxfm
      ) 
    
    #m <- as.data.frame(m)
})

```

Analysis of performance of all secondary standards, outliers have been removed by sigma (-10 to 10) and normalized Fm (-0.02 to 0.02), and only secondaries Fm > .1 used.

Normalized fm difference is defined as:

$\frac{Fm_{m}-Fm_{c}}{Fm_{c}}$

where $Fm_{m}$ is measured Fm and $Fm_{c}$ is consensus Fm.


# Summary table

## By System

```{r, echo=FALSE, message=FALSE,}

renderTable({
  #Make summary table
  out.s() %>%
    group_by(system) %>%
    summarize(
      nFm = mean(normFm),
      nFm.s = sd(normFm),
      sig = mean(sigma),
      ferr = mean(fmaxerr),
      N = n()
      )
  
}, digits = 4)


#print(table, floating=TRUE, type="html")
```


## By Secondary and System
```{r, echo=FALSE, message=FALSE, results='asis'}

renderTable({
#Make summary table
out.s() %>% 
  group_by(name, system) %>%
  summarise(
    fm.e = mean(fm_consensus),
    fm = mean(f_modern),
    fm.s = sd(f_modern),
    err = mean(merr),
    intrerr = intrErr(sd(f_modern), mean(merr)),
    d13c = mean(dc13),
    nFm = mean(normFm),
    nFm.s = sd(normFm),
    ferr = mean(fmaxerr),
    fintrerr = intrErr(sd(normFm), mean(fmaxerr)),
    sig = mean(sigma),
    sig.s = sd(sigma),
    N = n()
    )
}, digits=4)
#knitr::kable(secsum, digits = 4, caption = "Summary data for all secondaries")
```


# Histograms

```{r SigmaHistogram, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
renderPlot({
ggplot(out.s(), aes(sigma)) + geom_histogram() + 
  facet_grid(system ~ .) + 
  ggtitle(paste("Sigma Histogram"))
})
```


# Boxplots

Boxplots of secondaries ordered by Fm and separated by instrument. Boxes are 1st-3rd quartile, line is median, and whiskers indicate 1.5*IQD. 

```{r, SigmaBoxplots, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
renderPlot({
#sigma boxplots
p <- ggplot(out.s(), aes(name, sigma)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + facet_grid(system ~ .) + 
  ggtitle(paste("Sigma Boxplots")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
})

renderPlot({
#normfm boxplots
p <- ggplot(out.s(), aes(name, normFm)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + facet_grid(system ~ .) + 
  ggtitle(paste("Normalized Fm difference Boxplots")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

})
```

# System Precision

Looking at fractional error within samples to get an idea of system precision. This is error / fm. Internal (counting) error and external error compared. Ext/Int Precision Ratio looks at whether error is dominated by repeatability or counting statistics. I am not sure that these errors are comparable between systems, so please take with a grain of salt.

```{r precision,  echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}

renderPlot({
#   qplot(name,finterr, color=system, data=out.s(), geom="boxplot", ylim=c(0,.02), main="Internal precision") +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1))
#   qplot(name,fexterr, color=system, data=out.s(), geom="boxplot", ylim=c(0,.02), main="External precision") +
#     theme(axis.text.x = element_text(angle = 90, hjust = 1))
  qplot(name,fexterr/finterr, color=system, data=out.s(), geom="boxplot", main="Ext/Int Precision Ratio") +
    geom_hline(yintercept=1) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
  })
```



