Secondary standard analysis
========================================================

`r as.character(format(Sys.Date(), format="%B %d, %Y"))`





```{r Setup, echo=FALSE, warning=FALSE, message=FALSE}

#Load Libraries
require(ggplot2)
require(plyr)
require(dplyr)
require(knitr)
require(RODBC)

#Load files
source("~/R/dbconfig.R") #DB connection info
source("CalculateSecondaries.R") #Functions

#set parameters
from <- '2014-09-01'
to <- 'present' #present or date
sys <- 'both' #cfams, usams, ams1 or both
size <- c(40,300)

#Open DB connection
db <- odbcConnect(database, uid = uid, pwd = pwd)

###
#Make intcal table
###

#get intcal table
intcal <- sqlFetch(db, "intercal_samples")

#create factor of tiri_id, order by Fm
intcal <- within(intcal, name <- factor(tiri_id, levels = unique(tiri_id[order(fm_consensus, tiri_id)]),ordered = TRUE))

#Replace C-6 with new consensus from Xiaomei 2010
intcal$fm_consensus[intcal$rec_num == 1086] <- 1.5016

#add in OX-I, OX-II
ox <- read.csv("intcalox.csv")
intcal <- rbind(intcal, ox)

###
#get secondary data
###

out <- calcSecondaries(from, to, sys, intcal, db)

#Close DB
odbcClose(db)

#add %err
out$finterr <- out$f_int_error/out$f_modern
out$fexterr <- out$f_ext_error/out$f_modern
out$errrat <- out$merr/abs(out$fmd)

#select data by Fm, size, and date
out.c <- subset(out, f_modern > -.10 & f_modern < 1.6)

#clean out bad data points
out.c <- subset(out.c, is.na(q_flag))
out.c <- subset(out.c, sigma < 10 & sigma > -10)
out.c <- subset(out.c, normFm < 0.02 & normFm > -0.02)
out.s <- subset(out.c, gf_co2_qty > size[1] & gf_co2_qty < size[2])
```

Analysis of performance of all secondary standards for `r system` from `r from` to `r to`. Sample size is from `r size[1]` to `r size[2]`umol, outliers have been removed by sigma (-10 to 10) and normalized Fm (-0.02 to 0.02), and only secondaries Fm > .1 used.

* Mean Sigma for USAMS is `r mean(out.s$sigma[out.s$system=="USAMS"])`.
* Mean Sigma for CFAMS is `r mean(out.s$sigma[out.s$system=="CFAMS"])`.


# Summary table

## By System

```{r, echo=FALSE, message=FALSE,}

#Make summary table
syssum <- ddply(out.s, .(system), summarize,
                nFm = mean(normFm),
                nFm.s = sd(normFm),
                sig = mean(sigma),
                sig.s = sd(sigma),
                N = length(f_modern))

syssum

require(xtable)

table <- xtable(secsum)
digits(table) <- 4

#print(table, floating=TRUE, type="html")
```


## By Secondary and System
```{r, echo=FALSE, message=FALSE, results='asis'}

#Make summary table
secsum <- ddply(out.s, .(name, system), summarize,
                fm.e = mean(fm_consensus),
                fm = mean(f_modern),
                fm.s = sd(f_modern),
                nFm = mean(normFm),
                nFm.s = sd(normFm),
                sig = mean(sigma),
                sig.s = sd(sigma),
                N = length(f_modern))

require(xtable)

table <- xtable(secsum)
digits(table) <- 4

print(table, floating=TRUE, type="html")
```


# Histograms

```{r SigmaHistogram, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

#Sigma histogram
#p <- qplot(sigma, data=out.s, geom="histogram", xlim=c(-10,10))
#p + ggtitle(paste("Sigma Histogram, ", system, ", ", from))
ggplot(out.s, aes(sigma)) + geom_histogram() + 
  facet_grid(system ~ .) + 
  ggtitle(paste("Sigma Histogram, ", system, ", ", from))
```


# Boxplots

Boxplots of secondaries ordered by Fm and separated by instrument. Boxes are 1st-3rd quartile, line is median, and whiskers indicate 1.5*IQD. Normalized fm difference is defined as:

$\frac{Fm_{m}-Fm_{c}}{Fm_{c}}$

where $Fm_{m}$ is measured Fm and $Fm_{c}$ is consensus Fm.


```{r, SigmaBoxplots, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

#sigma boxplots
p <- ggplot(out.s, aes(name, sigma)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + facet_grid(system ~ .) + 
  ggtitle(paste("Sigma Boxplots, ", system, ", ", from)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

#normfm boxplots
p <- ggplot(out.s, aes(name, normFm)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + facet_grid(system ~ .) + 
  ggtitle(paste("Normalized Fm difference Boxplots, ", system, ", ", from)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```


## All secondaries by system

```{r, SystemBoxplots, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

#sigma boxplots
p <- ggplot(out.s, aes(system, sigma)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + ggtitle(paste("Sigma Boxplots for all secondaries by system")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

#normfm boxplots
p <- ggplot(out.s, aes(system, normFm)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + ggtitle(paste("Normalized Fm difference Boxplots for all secondaries by system")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```


## Selected secondaries

```{r, SelectedBoxplots, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

#Pick secondaries
s = filter(out.s, name %in% c("IAEA C-2", "TIRI I", "FIRI G", "IAEA C-6", "OX-I Solid", "OX-II"))

#normfm boxplots
p <- ggplot(s, aes(name, normFm)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + facet_grid(system ~ .) + 
  ggtitle(paste("Normalized Fm difference Boxplots")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

#normfm boxplots
p <- ggplot(s, aes(name, normFm)) + geom_hline(yintercept=0) + 
  geom_boxplot(aes(fill = factor(system)))#+ geom_jitter(aes(fill = factor(system))
p  + ggtitle(paste("Normalized Fm difference Boxplots")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```


# Fm vs Sigma

Sigma varies by Fm. First plot shows a regression through all data, 
which weights by N of secondaries, and second plot regression is 
through means of secondaries (whiskers show SD of mean).

```{r SigmavsRatio, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

#ratio vs sigma
p <- qplot(f_modern, sigma, color=system, shape=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + stat_smooth(method="lm", se=FALSE) +
  ggtitle(paste("Sigma vs Fm, ", system, ", ", from))
  #scale_colour_manual(values=cbPalette)

p <- qplot(fm, sig, color=system, data=secsum)
p + geom_hline(yintercept=0) + geom_point() +
  geom_errorbar(aes(ymin=sig-sig.s, ymax=sig+sig.s), width=.02) + 
  geom_smooth(method="lm") + 
  geom_point(size=3) + ggtitle(paste("Sigma vs Fm, ", system, ", ", from)) +
  scale_colour_manual(values=cbPalette)

```


# Fm vs Normalized Fm error

Another way of looking at the same. Y-axis is now normalized Fm error ( (Fm - consensus) / consensus ).

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
#norm ratio vs ratio
qplot(f_modern, normFm, color=system, data=out.s) +
  geom_hline(yintercept=0) + geom_point() + geom_smooth(method="lm") +
  ggtitle(paste("NormFm vs Fm, ", system, ", ", from))

ggplot(secsum, aes(x = fm, y = nFm, color=system)) +
  geom_hline(yintercept=0) + geom_point() + geom_smooth(method="lm") + 
  geom_errorbar(aes(ymin=nFm-nFm.s, ymax=nFm+nFm.s), width=.02) + geom_jitter(size=3) +
  ggtitle(paste("NormFm vs Fm, ", system, ", ", from))
```



#Sample size vs sigma

```{r SizeHistogram, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

ggplot(out.s, aes(gf_co2_qty)) + geom_histogram() + 
  facet_grid(system ~ .) + 
  ggtitle(paste("Size Histogram, ", system, ", ", from))
```

```{r sigmavsco2, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
p <- qplot(gf_co2_qty, sigma, color=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + #geom_smooth(method="lm") + 
  ggtitle(paste("Sigma vs umol CO2, ", system, ", ", from))

p <- qplot(gf_co2_qty, normFm, color=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + #geom_smooth(method="lm") + 
  ggtitle(paste("Normfm vs umol CO2, ", system, ", ", from))
```


# Date vs Sigma

```{r DateHistogram, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}

ggplot(out.s, aes(tp_date_pressed)) + geom_histogram() + 
  facet_grid(system ~ .) + 
  ggtitle(paste("Date Histogram, ", system, ", ", from))
```

```{r sigmavsdate,  echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
p <- qplot(tp_date_pressed, sigma, color=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + geom_smooth() + 
  ggtitle(paste("Sigma vs date, ", system, ", ", from))

p <- qplot(tp_date_pressed, normFm, color=system, data=out.s)
p + geom_hline(yintercept=0) + geom_point() + geom_smooth() + 
  ggtitle(paste("Normfm vs date, ", system, ", ", from))
```


# Individual Secondaries

Plot individual secondaries

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
#norm ratio vs ratio

plotSec <- function(sec, data, sys) {
  
  z = filter(data, name == sec, system == sys)
  m = mean(z$f_modern)
  sd = sd(z$f_modern)
  cons = z$fm_consensus[1]
  
  qplot(tp_date_pressed, f_modern, data = z) +
    geom_hline(yintercept = cons, color = "blue") +
    geom_hline(yintercept = m) +
    geom_hline(yintercept = m + sd, color = "gray") +
    geom_hline(yintercept = m - sd, color = "gray") +
    geom_point() +
    geom_errorbar(aes(ymin=f_modern-f_int_error, ymax=f_modern+f_ext_error)) + 
    ggtitle(paste("NormFm vs Fm", sys, sec))
}  

plotSec("IAEA C-2", out.s, "USAMS")
plotSec("IAEA C-2", out.s, "CFAMS")

```


#System Precision

Looking at fractional error within samples to get an idea of system precision. This is error / fm. Internal (counting) error and external error compared. Ext/Int Precision Ratio looks at whether error is dominated by repeatability or counting statistics. I am not sure that these errors are comparable between systems, so please take with a grain of salt.

```{r precision,  echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}

qplot(name,finterr, color=system, data=out.s, geom="boxplot", ylim=c(0,.02), main="Internal precision") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
qplot(name,fexterr, color=system, data=out.s, geom="boxplot", ylim=c(0,.02), main="External precision") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
qplot(name,fexterr/finterr, color=system, data=out.s, geom="boxplot", main="Ext/Int Precision Ratio") +
  geom_hline(yintercept=1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



