---
title: "NOSAMS Performance by Wheel"
author: "Brett Longworth"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r Setup, echo=FALSE, warning=FALSE, message=FALSE}
#TODO: check for DOC standards
#TODO: Add plots for normfm.mean or sigma.mean

#Load Libraries
library(dplyr)
library(knitr)
library(amstools)
library(ggplot2)
library(here)
library(lubridate)

theme_set(theme_light())
#set parameters- from, to, sys not used if loading from file
from <- '2016-01-24'
to <- 'present'
size <- c(40,300)
msig <- 10
mnfm <- .02
mferr <- .1

#Set digits for output
options(digits=4)

#Load QC data from file
load("qcData.rda")

data <- std %>% 
  filter(gf_co2_qty > 40, gf_co2_qty < 300, #Select size range
         tp_date_pressed >= from,
         rec_num != 53212,
         lab == "OSG", #Use only samples from the SPL
         is.na(q_flag), #Check for q_flag
         sigma < 10, sigma > -10, #Select reasonable sigmas
         #normFm < 0.02, normFm > -0.02, #Select reasonable Fm
         frep_err < 0.10,
         gf_devel == 0,
         is.na(gf_test)
         ) 
  
#Filter data (normalizing standards)
ox <- data %>% 
  filter(#primary == TRUE,
         rec_num %in% c(113385, 113386, 133143, 133144, 149822, 149823) #look at normalizing ox-I
  ) %>%
  group_by(wheel, system) %>%
  summarize(
    fm.s = sd(f_modern),
    sig = mean(sigma),
    sig.s = sd(sigma),
    rep_err.m = mean(rep_err),
    intrerr = intrErr(sd(f_modern), mean(rep_err)),
    N = length(f_modern)
  ) %>%
  mutate(date = mdy(substr(wheel, 6, 11))) %>%
  arrange(date)

# Filter data (all standards)
std <- data %>% 
  filter(f_modern > .1, f_modern < 1.6) %>%
  group_by(wheel, system) %>%
summarize(
  nFm = mean(normFm),
  nFm.sd = sd(normFm),
  sig = mean(sigma),
  sig.sd = sd(sigma),
  err = mean(rep_err),
  ferr = mean(frep_err),
  N = n()
  ) %>%
mutate(date = mdy(substr(wheel, 6, 11))) %>%
arrange(date)
```

# Summary

Performance of primary standards and all standards by wheel are the best metric I've come up with for machine performance. 

Reproducibility of standards is given by the standard deviation of the normalized fraction modern of all normalizing OX-I's on a wheel. 

Performance of all standards (secondary and primary) is given by the standard deviation of the sigma (Z-score) of all standards on a wheel. If the errors reported accurately reflect the variability of the data, this number should be 1.0. Values greater than 1 indicate underreporting of error.

Outliers (sigma > 10), poor performers (reported error > 0.1), small(ish) samples (<40umol), dead samples (Fm < 0.1), and samples not from the SPL have been removed to allow a more even comparison.

# Over time

This section presents these metrics for the period 2016 to present. 

## Normalizing standards

```{r}
ox %>% 
  ungroup() %>%
  group_by(system) %>% 
  summarize(fm.s = mean(fm.s, na.rm = TRUE),
            error = mean(rep_err.m)) %>%
  kable(caption = "SD of OX-I")
```

``` {r plots}
ggplot(ox, aes(date, fm.s, color = system)) + 
  geom_smooth() +
  geom_point() +
  scale_colour_brewer(type = "div", palette = "Set2") +
  ggtitle("SD of OX-I by wheel")
```

## All Standards

```{r}
std %>% 
  ungroup() %>%
  group_by(system) %>% 
  summarize(sig.sd = mean(sig.sd, na.rm = TRUE),
            sigma.mean = mean(sig, na.rm = TRUE),
            nFm.mean = mean(nFm, na.rm = TRUE),
            rep_err.mean = mean(err, na.rm = TRUE)) %>%
  kable(caption = "Summary Statistics for all standards")
```

```{r}
ggplot(std, aes(date, sig.sd, color = system)) +
  geom_smooth() +
  geom_point() +
  scale_colour_brewer(type = "div", palette = "Set2") +
  ggtitle("SD of standard sigmas by wheel")
```

```{r}
ggplot(std, aes(date, sig, color = system)) +
  geom_hline(yintercept = 0) +
  geom_smooth() +
  geom_point() +
  scale_colour_brewer(type = "div", palette = "Set2") +
  ggtitle("Mean of standard sigmas by wheel")
```

# Most recent data

This section presents the same metrics as above from May, 2019 to present. 

```{r}
ox <- filter(ox, date > '2019-05-01')
std <- filter(std, date > '2019-05-01')
```

## Normalizing Standards

```{r}
ox %>% 
  ungroup() %>%
  group_by(system) %>% 
  summarize(fm.s = mean(fm.s, na.rm = TRUE),
            error = mean(rep_err.m)) %>%
  kable(caption = "SD of OX-I")
```

``` {r, warning = FALSE}
ggplot(ox, aes(date, fm.s, color = system)) + 
  #geom_smooth() +
  geom_point() +
  scale_colour_brewer(type = "div", palette = "Set2") +
  ggtitle("SD of OX-I by wheel")
```

## All Standards

```{r}
std %>% 
  ungroup() %>%
  group_by(system) %>% 
  summarize(sig.sd = mean(sig.sd, na.rm = TRUE),
            sigma.mean = mean(sig, na.rm = TRUE),
            nFm.mean = mean(nFm, na.rm = TRUE),
            rep_err.mean = mean(err, na.rm = TRUE)) %>%
  kable(caption = "Summary Statistics for all standards")
```

```{r}
ggplot(std, aes(date, sig.sd, color = system)) +
  #geom_smooth() +
  geom_point() +
  scale_colour_brewer(type = "div", palette = "Set2") +
  ggtitle("SD of standard sigmas by wheel")
```

```{r}
ggplot(std, aes(date, sig, color = system)) +
  geom_hline(yintercept = 0) +
  geom_point() +
  scale_colour_brewer(type = "div", palette = "Set2") +
  ggtitle("Mean of standard sigmas by wheel")
```