---
output:
  html_document: default
  pdf_document: default
---

# Standard performance by wheel

`r as.character(format(Sys.Date(), format="%B %d, %Y"))`


## Load libraries and data

Using all primaries and secondaries, 2016 to present, Fm > 0.1, size > 500ug, SPL graphite only, sigma < 10, reported error < 10%.

```{r Setup, echo=TRUE, warning=FALSE, message=FALSE}

#Load Libraries
library(dplyr)
library(ggplot2)
library(knitr)
library(amstools)
library(stringr)
library(lubridate)
library(here)
 
#set parameters
from <- '2018-02-01'
to <- 'present' #present or date
sys <- 'both' #cfams, usams, ams1 or both
size <- c(40,300)
msig <- 10
mnfm <- .02
mferr <- .1

#Set digits for output
options(digits=4)

# Get fresh secondary data
#out <- getQCData(from, to, sys)

#Load QC data from file
load(here("qcData.rda"))

#Filter data
out.s <- filter(out, #primary == FALSE, # rec_num != 113385, #don't use normalizing ox-I
                f_modern > .1, f_modern < 1.6,
                tp_date_pressed >= as.Date(from),
                tp_date_pressed <= ifelse(to != 'present', to, Sys.Date()),
                gf_co2_qty > size[1], gf_co2_qty < size[2], #Select size range
                lab == "OSG", #Use only samples from the SPL
                is.na(q_flag), #Check for q_flag
                abs(sigma) < msig, #Select reasonable sigmas
                #abs(normFm) < mnfm, #Select reasonable Fm
                frep_err < mferr
              )
```


Aggregate standard data by wheel.

```{r, echo=TRUE, message=FALSE,}

#Make summary table
wheelsum <- out.s %>%
  group_by(wheel, system) %>%
  summarize(
    nFm = mean(normFm),
    nFm.sd = sd(normFm),
    sig = mean(sigma),
    sig.sd = sd(sigma),
    ferr = mean(frep_err),
    N = n()
    ) %>%
  mutate(date = mdy(substr(wheel, 6, 11))) %>%
  arrange(date)
```

## Summary 

### By system

#### Average of per-wheel sd of sigmas, by system.

```{r}
wheelsum %>% 
  ungroup() %>%
  group_by(system) %>% 
  summarize(sig.sd = mean(sig.sd, rm.na = TRUE)) 
```

#### Histogram of per-wheel sd of sigmas by system

```{r}
ggplot(wheelsum, aes(sig.sd)) +
  geom_histogram() +
  facet_grid(system ~ .)
```

#### By number of standards

```{r}
ggplot(wheelsum, aes(N, sig.sd, color = system)) +
  geom_smooth() +
  geom_point()
```

## Over time

### SD of sigmas

```{r}
ggplot(wheelsum, aes(date, sig.sd, color = system)) +
  geom_smooth() +
  geom_point()
```

### SD of normFm

```{r}
ggplot(wheelsum, aes(date, nFm.sd, color = system)) +
  geom_smooth() +
  geom_point()
```

### mean sigma

```{r}
ggplot(wheelsum, aes(date, sig, color = system)) +
  geom_smooth() +
  geom_point()
```

## All wheels
```{r}
# display full table
knitr::kable(wheelsum, digits = 5, caption = "Summary data for secondaries")
```



