---
runtime: shiny
output: html_document
---


Secondary standard analysis
========================================================

`r as.character(format(Sys.Date(), format="%B %d, %Y"))`



```{r Setup, echo=FALSE, warning=FALSE, message=FALSE}

#Load Libraries
library(dplyr)
library(ggplot2)
library(knitr)
library(amstools)

#Set digits for output
options(digits=4)

# Get fresh secondary data
#out <- getQCData(from, to, sys)

#Load QC data from file
load("./qcData.rda")

out <- filter(out,
        primary == FALSE, #don't use normalizing ox-I
        lab == "OSG", #Use only samples from the SPL
        is.na(q_flag) #Check for q_flag
)
```

## Choose data

Select data source.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

# out <- reactive({
#   if (input$data == "qc") {
#     getQCTable(from, to)
#   } else if (input$data == "intcal") {
#     out
#   } else if (input$data == "standards") {
#     stds
#   }
# })
```


## Filter data

use these widgets to filter secondary data as desired

```{r echo = FALSE}
selectInput('data',
            label = 'Data Source', 
            c("qc", "intcal", "standards"))
dateRangeInput('date',
               label = 'Date Range',
               start = Sys.Date() - 90, 
               end = Sys.Date(),
               max = Sys.Date())
sliderInput("size", "Graphite Size (umol)",
            1, 500, value = c(40,300))
sliderInput("fm", "Fm Range",
            0, 2, value = c(.1,1.6), step = 0.05)
sliderInput("sigma", "Max Sigma",
            0, 12, value = 10)
sliderInput("nfm", "Max norm Fm",
            0, 0.1, value = 0.02)
sliderInput("fme", "Max reported error",
            0, 0.05, value = 0.05)


out.s <- reactive({
    # Due to dplyr issue #318, we need temp variables for input values
    mindate <- input$date[1]
    maxdate <- input$date[2]
    minsize <- input$size[1]
    maxsize <- input$size[2]
    minfm <- input$fm[1]
    maxfm <- input$fm[2]
    sig <- input$sigma
    nfm <- input$nfm
    fme <- input$fme

    # Apply filters
    out %>%
      filter(
        as.Date(tp_date_pressed) >= as.Date(mindate),
        as.Date(tp_date_pressed) <= as.Date(maxdate),
        gf_co2_qty >= minsize,
        gf_co2_qty <= maxsize,
        fm_consensus >= minfm,
        fm_consensus <= maxfm,
        sigma < sig, sigma > -sig, #Select reasonable sigmas
        normFm < nfm, normFm > -nfm, #Select reasonable Fm
        frep_err < fme
        )
})

```

analysis of performance of all secondary standards, outliers have been removed by sigma (-10 to 10) and normalized Fm (-0.02 to 0.02), and only secondaries Fm > .1 used.

normalized fm difference is defined as:

$\frac{Fm_{m}-Fm_{c}}{Fm_{c}}$

where $Fm_{m}$ is measured Fm and $Fm_{c}$ is consensus Fm.


# Summary table

## By System

```{r, echo=FALSE, message=FALSE,}

renderTable({
  #Make summary table
  out.s() %>%
    group_by(system) %>%
    summarize(
      nFm = mean(normFm),
      nFm.s = sd(normFm),
      sig = mean(sigma),
      ferr = mean(frep_err),
      N = n()
      )
  
}, digits = 4)


#print(table, floating=TRUE, type="html")
```


## By Secondary and System
```{r, echo=FALSE, message=FALSE, results='asis'}

renderTable({
#Make summary table
out.s() %>% 
  group_by(name, system) %>%
  summarise(
    fm.e = mean(fm_consensus),
    fm = mean(f_modern),
    fm.s = sd(f_modern),
    err = mean(rep_err),
    d13c = mean(dc13),
    nFm = mean(normFm),
    nFm.s = sd(normFm),
    ferr = mean(frep_err),
    sig = mean(sigma),
    N = n()
    )
}, digits=4)
```


# Histograms

```{r SigmaHistogram, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
renderPlot({
ggplot(out.s(), aes(sigma)) + geom_histogram(bins = input$bins) + 
  facet_grid(system ~ .) + 
  ggtitle(paste("Sigma Histogram"))
})
sliderInput("bins", "number of histogram bins",
            1, 100, value = 30)
```


# Boxplots

boxplots of secondaries ordered by Fm and separated by instrument. Boxes are 1st-3rd quartile, line is median, and whiskers indicate 1.5*IQD. 

```{r, SigmaBoxplots, echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
renderPlot({
#sigma boxplots
p <- ggplot(out.s(), aes(name, sigma, color=process)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + facet_grid(system ~ .) + 
  ggtitle(paste("Sigma Boxplots")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
})

renderPlot({
#normfm boxplots
p <- ggplot(out.s(), aes(name, normFm, color=process)) + geom_hline(yintercept=0) + 
  geom_boxplot() + geom_jitter()
p + facet_grid(system ~ .) + 
  ggtitle(paste("Normalized Fm difference Boxplots")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

})
```

