---
output: html_document
---
Primary standard analysis
========================================================

`r as.character(format(Sys.Date(), format="%B %d, %Y"))`





```{r Setup, echo=FALSE, warning=FALSE, message=FALSE}

#Load Libraries
library(dplyr)
library(knitr)
library(RODBC)
library(ggplot2)

#Load files
source("~/R/dbconfig.R") #DB connection info
source("CalculateSecondaries.R") #Functions

#set parameters- from, to, sys not used if loading from file
from <- '2014-09-01'
to <- 'present' #present or date
sys <- 'both' #cfams, usams, ams1 or both
size <- c(40,300)

#Set digits for output
options(digits=4)

# Get fresh secondary data
#out <- getQCData(from, to, sys)

#Load QC data from file
load("qcData.rda")

#Filter data
out.s <- out %>% 
  filter(primary == TRUE,
         rec_num %in% c(113385, 113386), #look at normalizing ox-I
         f_modern > .1, f_modern < 1.6,
         gf_co2_qty > size[1], gf_co2_qty < size[2]) %>% #Select size range
  mutate(month = ordered(months(tp_date_pressed), 
    c("September","October","November","December","January", "February", "March", "April", "May")),
    cnterr = 1 / sqrt(counts))
  
```

Analysis of performance of primary standards for `r sys` from `r from` to `r to`. Sample size is from `r size[1]` to `r size[2]`umol, outliers have been removed by sigma (-10 to 10) and normalized Fm (-0.02 to 0.02).

* Mean Sigma for USAMS is `r mean(out.s$sigma[out.s$system=="USAMS"])`.
* Mean Sigma for CFAMS is `r mean(out.s$sigma[out.s$system=="CFAMS"])`.

Normalized fm difference is defined as:

$\frac{Fm_{m}-Fm_{c}}{Fm_{c}}$

where $Fm_{m}$ is measured Fm and $Fm_{c}$ is consensus Fm.


# Summary table


```{r, echo=FALSE, message=FALSE, results='asis'}

#Make summary table
secsum <- out.s %>% 
  group_by(name, system) %>%
  summarise(
    fm.e = mean(fm_consensus),
    fm.m = mean(f_modern),
    fm.s = sd(f_modern),
    merr.m = mean(merr),
    d13c = mean(dc13, na.rm = TRUE),
    sig = mean(sigma),
    sig.s = sd(sigma),
    intrerr = intrErr(sd(f_modern), mean(merr)),
    N = n()
    )

knitr::kable(secsum, digits = 4, caption = "Summary data for all primaries")

```

# System Precision

Looking at fractional error within samples to get an idea of system precision. This is error / fm. Internal (counting) error and external error compared. Ext/Int Precision Ratio looks at whether error is dominated by repeatability or counting statistics. I am not sure that these errors are comparable between systems, so please take with a grain of salt.

```{r precision,  echo=FALSE, warning=FALSE, message=FALSE, fig.width=8, fig.height=5}

ggplot(out.s, aes(cnterr, finterr)) +
  geom_point(aes(shape = system, color = system), alpha=.5) + scale_shape(solid = FALSE) +
  scale_x_continuous(limits = c(.00125, .0025)) + 
  ggtitle("Internal precision") 
ggplot(out.s, aes(le12c, finterr)) +
  geom_point(aes(shape = system, color = system), alpha=.5) + scale_shape(solid = FALSE) +
  #scale_y_continuous(limits = c(.00125, .00275)) + 
  ggtitle("Internal precision") 
ggplot(out.s, aes(cnterr, fexterr)) +
  geom_point(aes(shape = system, color = system), alpha=.5) + scale_shape(solid = FALSE) +
  scale_x_continuous(limits = c(.00125, .0025)) + 
  #scale_y_continuous(limits = c(.00125, .00275)) + 
  ggtitle("External precision") 
ggplot(out.s, aes(le12c, fexterr)) +
  geom_point(aes(shape = system, color = system), alpha=.5) + scale_shape(solid = FALSE) +
  #scale_y_continuous(limits = c(.0015, .0025)) + 
  ggtitle("External precision") 
ggplot(out.s, aes(cnterr, fexterr/finterr)) +
  geom_point(aes(shape = system, color = system), alpha=.3) + scale_shape(solid = FALSE) +
  scale_x_continuous(limits = c(.00125, .0025)) + 
  scale_y_continuous(limits = c(.99, 1.01)) + 
  ggtitle("Ext/Int Precision Ratio") +
  geom_hline(yintercept=1) 
ggplot(out.s, aes(le12c, fexterr/finterr)) +
  geom_point(aes(shape = system, color = system), alpha=.3) + scale_shape(solid = FALSE) +
  scale_y_continuous(limits = c(.99, 1.01)) + 
  ggtitle("Ext/Int Precision Ratio") +
  geom_hline(yintercept=1) 
```

## Interesting points

The distribution of the ratio of external to internal errors looks gaussian with a huge peak tacked on at 1:1.

```{r}
ggplot(out.s, aes(fexterr/finterr)) +
  geom_density() + facet_grid(system ~ .) +
  #scale_y_continuous(limits = c(.99, 1.01)) + 
  ggtitle("Ext/Int Precision Ratio") +
  geom_vline(xintercept=1) 
```


Let's look at points where external error < internal error, ie, points that don't make statistical sense.


```{r}

out.i <- filter(out.s, fexterr/finterr < 1) 
qplot(finterr, fexterr, data=out.i, color = system)
```

