---
title: "Analysis of a secondary following Xiaomei 2010"
author: "BEL"
date: "01/11/2016"
output: html_document
---

This script examines a secondary standard using the methods used in Xiaomei 
Xu's 2010 paper, "Is the consensus value of ANU sucrose (IAEA C-6) too high".
  
Data pulled from no_os by rec_num.

## Get the data

```{r echo=FALSE, message=FALSE}
#Load Libraries
library(RODBC)
library(ggplot2)
library(dplyr)
library(knitr)

digits=4
#Load files
source("~/R/dbconfig.R") #DB connection info
source("CalculateSecondaries.R") #Functions

#set parameters- from, to, sys not used if loading from file
from <- '2014-09-01'
to <- 'present' #present or date
sys <- 'both' #cfams, usams, ams1 or both

#Pull the data
db <- odbcConnect(database, uid = uid, pwd = pwd)
ss <- getSecondary(1086, from, to, sys, db)
odbcClose(db)

#add reported error
ss <- mutate(ss, max_err = pmax(f_int_error, f_ext_error))
```

## Outlier tests

Filter out the outliers using the two outlier tests from Rozanski et al. (1992).

* Omit values $< H_L-3(H_U-H_L)$ or $> H_L+3(H_U-H_L)$ where $H_L$ and $H_U$
are the lower and upper quartiles, respectively.

* $|(Fm-m)/\sigma|<2$ where $Fm$ is the measurement, $m$ is the median after outliers are removed as above, and $\sigma$ is the reported error of the measurement.

```{r outliers}
# 1st outlier test
q <- quantile(ss$f_modern, probs = c(.25, .75), names = FALSE)
oh <- q[2]+3*(q[2]-q[1])
ol <- q[1]-3*(q[2]-q[1])

ss <- ss %>% filter( f_modern < oh,
                     f_modern > ol)
                     
# second outlier test
m <- median(ss$f_modern)
ss <- ss %>% filter(abs((f_modern - m)/max_err) < 2)
```

Here's the data so far...

```{r, echo=FALSE, message=FALSE}
qplot(f_modern, data=ss)

kable(select(ss, tp_num, tp_date_pressed, wheel_id, gf_co2_qty, f_modern, max_err))
```

## Consensus value estimation

Using the method in Rozanski et al. (1992), consensus value is calculated as the weighted average ($X_w$) of the data remaining after removing outliers. The uncertainty is determined using the estimated standard error.
```{r consensus}

# weighted average function. Need to test this.
weighted.average <- function(x, w) {
  sum(x/w^2)/sum(1/w^2)
}

# estimated standard error
ese <- function(x, w) {
  n <- length(x)
  x.m <- weighted.average(x, w)
  e <- sqrt( sum((x-x.m)^2/w^2)/n)
  
e * sqrt(sum(1/w^2))
}

v <- sum(wt * (x - xm)^2)
```

```{r}
#Make summary table
syssum <- ss %>%
  #group_by(system) %>%
  summarize(
    nFm = mean(f_modern),
    nFm.s = sd(f_modern),
    nFm.e = se(f_modern),
    ferr = mean(max(f_int_error,f_ext_error)),
    N = n()
    )

knitr::kable(syssum, digits = 5, caption = "Summary data for secondaries")


```

